The \dealii{} Library, Version 9.0

### 2018-04-16 9.0/paper.tex
Add funding acknowledgement
Update entries for clang-tidy and coverity

\item \dealii{} has made extensive use of both the clang-tidy and coverity
      static analysis tools for detecting bugs and other issues in the code.
      %% TODO is there somewhere we can cite for either of these tools? It would
      %% be nice to recognize the department of homeland security for offering
      %% coverity.
      %% TODO at the time of writing this coverity is down; get an issue count
      %% when it is back online.

@@

D.~Arndt was partially supported by the German Research Foundation (DFG) under the
project ``High-order discontinuous Galerkin for the exa-scale'' (ExaDG) within the
priority program ``Software for Exascale Computing'' (SPPEXA).

@@

% J-P.~Pelteret was supported by the European Research Council (ERC) through the Advanced Grant 289049 MOCOPOLY.
%
B.~Turcksin: This material is based upon work supported by the U.S. Department of
Energy, Office of Science, under contract number DE-AC05-00OR22725.

>>>>

\item \dealii{} has made extensive use of both the Clang-Tidy \cite{clang-tidy}
  and Coverity Scan \cite{coverity} static analysis tools for detecting bugs
  and other issues in the code. In total around, 260 issues were detected and
  fixed using the latter tool.
      %% > Is there somewhere we can cite for either of these tools? It would
      %% > be nice to recognize the department of homeland security for offering
      %% The contract with homeland security was completed in 2009.

@@

D.~Arndt was supported by the German Research Foundation (DFG) under the
project ``High-order discontinuous Galerkin for the exa-scale'' (ExaDG) within the
priority program ``Software for Exascale Computing'' (SPPEXA).

@@

J-P.~Pelteret was supported by the European Research Council (ERC) through the Advanced Grant 289049 MOCOPOLY.

B.~Turcksin: This material is based upon work supported by the U.S. Department of
Energy, Office of Science, under contract number DE-AC05-00OR22725.
